Greeedy heuristic

### 2018-05-29 R/OptiPlan_presentation/proposal_fr.Rmd
Added ret analysis and heuristic explanation.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('scripts/params.R')
source('scripts/import_results.R')
source('diagrams/cases.R')
source("diagrams/architecture.R")
source("diagrams/functionalities.R")
source('diagrams/exampleDT.R')
source('diagrams/gantt_tasks.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
exp_directory2 = PATHS[['experiments']] %>% paste0('201802061201/')
gantt <- print_solution(exp_directory, max_resources = 10, width="100%", height="500px")
gantt_tasks <- print_tasks(exp_directory2, width="100%", height="200px", max_tasks = 5)
graphs_rem <- graph_remaining(exp_directory)
table_rem <- table_remaining(exp_directory)
html_output <- knitr::opts_knit$get("rmarkdown.pandoc.to") %in% c("slidy", 'html')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('functions/params.R')
source('functions/import_results.R')
source('diagrams/cases.R')
source("diagrams/architecture.R")
source("diagrams/functionalities.R")
source('functions/exampleDT.R')
source('functions/gantt_tasks.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
exp_directory2 = PATHS[['experiments']] %>% paste0('201802061201/')
gantt <- print_solution(exp_directory, max_resources = 10, width="100%", height="500px")
gantt_tasks <- print_tasks(exp_directory2, width="100%", height="200px", max_tasks = 5)
graphs_rem <- graph_remaining(exp_directory)
table_rem <- table_remaining(exp_directory)
html_output <- knitr::opts_knit$get("rmarkdown.pandoc.to") %in% c("slidy", 'html')
```

### 2018-05-29 R/diagrams/heuristic/heuristic.Rmd
Added ret analysis and heuristic explanation.

---
title: "heuristic1"
author: "Franco Peschiera"
date: "January 9, 2018"
output:
    html_document:
        # css: ./../../css/baobab.css
---

```{r setup, include=FALSE}
source("heuristic.R")
source("../../functions/params.R")

knitr::opts_chunk$set(echo = FALSE)
path <- paste0(PATHS['r_project'], 'diagrams/heuristic/')
```

@@

With the candidate and the task we do the following:

    for every task:
        1. calculate candidates.
        for each candidate until we run out of candidates or we satisfy task's needs:
            1. find available periods.
            Until we run out of periods:
                1. we check if we can assign it (checking remaining time and elapsed time). 
                    * If we can't: we tag the aircraft as "in need of a maintenance'.
                    * if we can: we assign the task.
                2. After assigning a task: we update the remaining and elapsed times for the aircraft.
            1. If we tagged the aircraft as in need of maintenances: we update.

@@

    1. we check if we can reserve 6 continous months of maintenance.
        * if we can: we do it (and continue assigining tasks to the aircraft).
        * if we cannot: we go to the next candidate.
    2. After assigning a maintenance: we update the remaining and elapsed times for the aircraft.

@@

```{r, echo=FALSE}
graph_solve(paste0(path, 'heur_solve.csv'), height=500)
```

@@

```{r, echo=FALSE}
graph_fill_mission(paste0(path, 'heur_fill_mission.csv'), height=700)
```

@@

>>>>

---
title: "Greeedy heuristic"
date: "January 9, 2018"
output:
    html_document:
        toc: yes
        css: ./../../../css/baobab_docs.css
---

```{r setup, include=FALSE}
source("heuristic.R")
functions_dir <- '../../functions/'

source(paste0(functions_dir, "params.R"))
source(paste0(functions_dir, 'import_results.R'))

exp_directory = PATHS[['experiments']] %>% paste0('201805241334/')

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
path <- paste0(PATHS['r_project'], 'diagrams/heuristic/')
```

@@

    for every task:
        Calculate candidates.
        Repeat:
            Sort candidates.
            Get first candidate
            Find available periods.
            Repeat:
                Get first period.
                Can we assign task?
                    no: we tag it "in need of maintenance'.
                    yes: we assign the task.
                After assigning a task: we update the counters.
            If we tagged the aircraft as in need of maintenances: 
                Execute maintenance assignment

@@

    good candidate slot maintenance?
        yes: we give maintenance in slot.
        no: we go to the next candidate.
    if maintenance was assigned:
        Update the remaining and elapsed times for the aircraft.

@@

```{r, echo=FALSE, warning=FALSE}
graph_solve(paste0(path, 'heur_solve.csv'), height=500)
```

@@

```{r, echo=FALSE, warning=FALSE}
graph_fill_mission(paste0(path, 'heur_fill_mission.csv'), height=700)
```

@@

## Example planning

```{r, echo=FALSE}
print_solution(exp_directory)
```
